Technical Report

### 2018-03-23 fully-abstract-comp/technical-report.tex
updated static region to require values in untrusted value relation
fixed compilation error
Explanation about source language contextual equivalence.

>>>>

Note that we define source language contextual equivalence with respect to contexts that are not in $\ta$.
This means that they are unable to perform calls.
We believe this fits with the goal of this work: allow programmers (or better: authors of previous compiler passes) to reason about their target language programs under a special perspective, where all calls can be interpreted as calls that actually behave in a well-bracketed way by the operational semantics.
This special perspective is defined by overlaying a different operational semantics on the existing code: the source language semantics.
The fact that source contexts cannot make calls themselves is no problem: authors of previous compiler passes should only be able to take the perspective that their own calls are guaranteed to be well-bracketed.
It does not matter for them whether calls in the rest of the system are guaranteed to be well-bracketed.
Note also that if the trusted code hands out closures, the context can still invoke them with an xjmp, rather than a call.
That xjmp can even be the one in the implementation of call if the context uses that implementation. 
This works perfectly fine, except that the context does not get any well-bracketedness guarantees, but that doesn't matter.
